---
title: "OkalaR Package Tutorial"
author: "Adam Varley"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(okalaR)
library(jsonlite)
```

# Getting Started

This tutorial demonstrates how to use the `okalaR` package to interact with the Okala dashboard API.

## Authentication

Your API key is found in your project settings on the Okala dashboard: [https://dashboard.okala.io/](https://dashboard.okala.io/)

```{r auth, eval=FALSE}
api_key <- 'your_api_key_here' # Replace with your actual API key
headers <- auth_headers(api_key, okala_url = "https://api.dashboard.okala.io/api/")
```

## Get Project Information

```{r get-project, eval=FALSE}
get_project(hdr = headers)
```

## Get Station Information

```{r get-stations, eval=FALSE}
stations <- get_station_info(hdr = headers, datatype = "video")
plot_stations(stations)
```

## Get Media Labels for Sensors

```{r get-media-labels, eval=FALSE}
media_labels <- get_media_assets(hdr = headers,
                                 datatype = "video",
                                 psrID = stations$project_system_record_id)
```

## Get Project Labels

```{r get-project-labels, eval=FALSE}
project_camera_labels <- get_project_labels(hdr = headers, labeltype = 'Camera')
```

## Get IUCN Labels

```{r get-iucn-labels, eval=FALSE}
labelled_data <- getIUCNLabels(hdr = headers,
                              limit = 2000,
                              offset = 0,
                              search_term = 'Domestic horse')
```

## Add Labels to IUCN Database

```{r add-iucn-labels, eval=FALSE}
example_data <- 'data/domestic_animals.json'
example_data <- readLines(example_data)
example_data <- jsonlite::fromJSON(example_data)
example_data <- jsonlite::fromJSON(example_data)
example_data <- example_data[example_data$species != 'NA', ]
example_data$class <- example_data$class_
example_data$extant_country_list <- NA
example_data$iucn_redlist_status[example_data$iucn_redlist_status == 'Extinct In The Wild'] <- 'Extinct in the Wild'
example_data$iucn_redlist_status <- gsub('Lower Risk/', '', example_data$iucn_redlist_status)
example_data$iucn_redlist_status <- gsub('Conservation Dependent', 'Not Evaluated', example_data$iucn_redlist_status)

add_IUCN_labels(hdr = headers, labels = example_data, chunksize = 500)
```

## Update Existing Labels on the Platform

```{r update-labels, eval=FALSE}
new_label_id <- project_camera_labels[which(project_camera_labels$common_name == 'Uneven-toothed Rat'), 'label_id']
segment_record_to_change <- data.frame(segment_record_id_fk = media_labels[1, 'segment_record_id'], label_id_fk = 1)
submission_frame <- data.frame(segment_record_id_fk = segment_record_to_change, label_id_fk = new_label_id, number_of_individuals = 1)
push_new_labels(hdr = headers, submission_records = submission_frame, chunksize = 30)
```
